---
title: "STAT 450 Assignment 1"
author: "Christian Samson"
date: '2018-01-11'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## About Me

I'm a 4th year STAT major currently taking STAT 443 and STAT 450, hopefully completing my degree this semester. I did two co-op terms in 2016, one at a children's hospital in Montreal and one at an online lending company here in Downtown Vancouver. My co-op at the children's hospital was a similar style project to STAT 450, in that I had to work on my own to explore and analyze data given to me by 'a client' (my boss) and I really look forward to doing something similar here.

## My Favorite Equation

My favorite equation is the quadratic formula.

$$\frac{-b \pm \sqrt{b^2 -4ac}}{2a}$$
It's my favorite because it's not exactly a trivial or simple equation, but it can help you easily find the solutions of a polynomial.

## My Favorite Dataset

My favorite dataset is the 'airquality' dataset in R. It contains daily air quality measurements in New York from May to September of 1973.

```{r airquality, echo=TRUE}
head(airquality, n=5)
temps <- ts(airquality$Temp, start = c(1973,121), frequency = 365)
ts.plot(temps, main="Max Temperature at Laguardia Airport in NYC from 5/1/73 to 9/30/73", ylab="Degrees (F)")
```



